\LARGE\textbf{Designing Studies and Evaluating Research Results:\\ Type M and Type S Errors for\\ Pearson Correlation Coefficient }

### 2021-09-03 Documents/Paper_main/Paper_main.Rnw
add packages for tinytex
fix path

@@

<<Plot_cohen,warning=F, fig.pos="!h", fig.align="center", fig.height=3, fig.width=6, fig.cap="The behaviour of Type M and Type S errors as a function of statistical power in the case of Cohen's \\emph{d}. Note that the four lines are overlapping." >>=
load("../../data/data_cohen.rda")

@@

<<Plot_rho,warning=F, fig.pos="!h", fig.align="center", fig.height=3, fig.width=6, fig.cap="The behaviour of Type M and Type S errors as a function of statistical power in the case of Pearson's correlation $\\rho$." >>=
load("../../data/data_conditions_rho.rda")

>>>>

\usepackage{grfext}  % added for tinytex
\usepackage{framed}  % added for tinytex

@@

<<Plot_cohen,warning=F, fig.pos="!h", fig.align="center", fig.height=3, fig.width=6, fig.cap="The behaviour of Type M and Type S errors as a function of statistical power in the case of Cohen's \\emph{d}. Note that the four lines are overlapping." >>=
load("../../Data/data_cohen.rda")

@@

<<Plot_rho,warning=F, fig.pos="!h", fig.align="center", fig.height=3, fig.width=6, fig.cap="The behaviour of Type M and Type S errors as a function of statistical power in the case of Pearson's correlation $\\rho$." >>=
load("../../Data/data_conditions_rho.rda")
